---
title: "Final Presentation"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
editor_options: 
  chunk_output_type: console
runtime: shiny
author: "Group 5"
date: "April 23, 2018"
---
```{r setup, include=FALSE}
library(tidyverse)
library(flexdashboard)
library(plotly)
library(tidyr)
library(ggmap)
```

```{r}
con <- dplyr::src_mysql(
  host = "ba-isdsclass-programdev.lsu.edu",
  port = 3306,
  user = 'student',
  password = 'student',
  dbname = "isds_3105") 
```

```{r}
commencement <- tbl(con, 'commencement')
alumnus <- tbl(con, 'alumnus')
currentPosition <- tbl(con, 'currentPosition')
location <- tbl(con, 'location')
internship <- tbl(con,'internship')
organization <- tbl(con,'organization')
title <- tbl(con,'title')
college <- tbl(con, 'college')
graduation <- tbl(con, 'graduation')
graduationTitle <- tbl(con, 'graduationTitle')
```

```{r}
major <-  graduation %>% left_join(graduationTitle, by = c('graduationId', 'graduationId')) %>% left_join(title, by = c('idTitle', 'idTitle')) %>% select(graduationId, majorName)

h <- major %>% left_join(currentPosition, by = c('graduationId', 'graduationId')) %>% select(graduationId, majorName, locationId) %>% left_join(location, by =c('locationId', 'locationId')) 

#2,835 have locationId's the rest are null. However, you can make the assumption to the organizationId accordingly. 
```

```{r}
#This drops all elements with NAs as locationId
h1 <- h %>% collect() %>% drop_na(locationId)
```

```{r}
#This joins mapdata with our table so we can make a map. Its has over 1 million element though so im not sure if its 100% correct.

states <- map_data("state")
h2 <- mutate(h1, region = tolower(stateFull)) 
#right_join(h2,states, by = c('region' = 'region')) -> mmap
```

```{r}
statela <- map_data("county") %>% subset(., region %in% c("louisiana"))
```

```{r}
h2 %>% group_by(majorName, region) %>% summarise(total = n()) -> countstate
left_join(countstate,states, by = c('region' = 'region')) -> test1
h2la <- h2 %>% subset(., region %in% c("louisiana"))
h2la %>% group_by(majorName, city) %>% summarise(total = n()) -> lacountstate
h2la %>% group_by(majorName) %>% summarise(total = n()) -> countstatela
```

```{r}
mappingFunc <- function(df, name) {
  if (!( name  %in% unique(df$majorName))) stop('You need to pick a Major within those available in the dataset')
  ggplot(filter( df , majorName == name )) +
    geom_polygon(data = states, aes(x=long, y=lat, group = group), color = "black") +
    coord_fixed(1.3) +
    guides(fill=F)+
    geom_polygon(aes(x = long, y = lat, group = group, fill = total), color = "black") + 
    coord_fixed(1.3) +
    guides(fill=F) +
    ggtitle( name )
}
```

```{r}

mplottingFunc <- function(df, name) {
  if (!( name  %in% unique(df$majorName))) stop('You need to pick a Major within those available in the dataset')
  ggplot(filter( df , majorName == name )) +
    geom_col(aes(city, total))
}
```

```{r}
mplottingFunc1 <- function(df, name) {
  if (!( name  %in% unique(df$majorName))) stop('You need to pick a Major within those available in the dataset')
  ggplot(filter( df , majorName == name )) +
    geom_col(aes(region, total))
}
```



 
Inputs {.sidebar}
-------------------------------------

```{r}
MajorNames <- setNames(unique(h2$majorName), unique(h2$majorName)) %>% as.list()
 selectInput("Major", label = h4("Major"), 
    choices = MajorNames, 
    selected = 'Construction Management')
```

Column {data-width=600}
-------------------------------------
###Research Question
What state is a graduate most likely to live in based on the major they graduated with? e.g. What majors are higest demand in each state?

###Users
- Departments at LSU
  --- Interested in the placement of their students
- LA Office of Student Financial Assistance
  --- Determine if TOPS funding certain majors is econmically worthwile based on graduate retention in        Louisiana
- Prospective students
  --- Evaluating LSU majors based on where they can get job
- LSU Seniors
  --- Applying for jobs

###Limitations
1. Flexdashboard - more knowledge on formatting would have allowed for better presentation of material.
2. Geospacial visualization
3. More instances of location data in the data set

###Findings
Most majors stayed in Louisiana.
Besides Louisiana, Texas receives the most LSU graduates.
Engineering majors tend to leave the state.
Of the graduates that stayed in Louisiana, most reside in Baton Rouge with New Orleans housing the second most.

###A map to visualize the locations people reside in after graduating with the selected major
```{r}
renderPlot({
  mappingFunc(test1, input$Major)
})
```

###The top five cities in Louisiana people reside in with the selected degree
```{r}
renderPlot({
 lacountstate %>% 
    arrange(desc(total)) %>%
    slice(1:5) %>% mplottingFunc(., input$Major)
})
```

###The top five states people reside in after graduating with the selected major
```{r}
renderPlot({
  countstate %>%
    arrange(desc(total)) %>%
    slice(1:5) %>% mplottingFunc1(., input$Major)
})
```

###The top five majors that stay in Louisiana after graduation
```{r}
#top 5 highest demand majors in la
renderPlot({
  countstatela %>% 
      arrange(desc(total)) %>%
      slice(1:5) %>%
  ggplot() +
      geom_col(aes(majorName, total))
})
```


